Co-moving stars in \textsl{Gaia DR1}:\\ An abundance of very wide separation co-moving pairs

### 2017-02-03 paper/ms.tex
figure 5 updated

To date, thousands of candidate co-moving star pairs have been identified by
searching for stars with common proper motions
(\citealt{Poveda:1994aa,Allen:2000aa,Chaname:2004aa,Lepine:2007aa,Alonso-Floriano:2015aa}).
Here, we use the recent first data release of \gaia\ which includes precise distances,
enabling us to ask whether two stars share the same \emph{physical (3D) velocity} rather than
just the projections in the proper motion space.

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{glon_d_pie.pdf}
  \end{center}
  \caption{%
    Panoramic view of co-moving pairs of stars. This is a cylindrical
    projection of onto the Galactic plane. The angle is the Galactic
    longitude, and the radius is $\hat d\cos b$ in pc where $\hat d$ is the point-estimate
    of distance using \eqname~\ref{eq:dist}.
    Pairs in connected components of sizes less than 5 are connected by gray lines.
    Pair in connected components of size $\geq 5$ are plotted with a unique random color,
    and their nodes (stars) are highlighted with small black circles.
    We also show the positions of known Milky Way star clusters
    from \citet{Kharchenko:2016aa} as light blue circles,
    and stars in OB associations from \citet{de-Zeeuw:1999aa} as
    gray circles.
    Some of the larger connected components are clearly associated with known
    clusters, but we also discover quite a few new co-moving groups.
    \label{fig:glon_d_pairlines}}
\end{figure*}

@@

In this section, we describe our catalog of candidate co-moving pairs of stars.
For 13,058 pairs (10,606 unique stars) found in this work.
The catalog is composed of three tables of stars, pairs, and groups.
We summarize the content of each table in Table~\ref{tab:table_meta}, and
the relationships between the tables in Figure~\ref{fig:schema}.
The star table contains all 10,606 stars that has at least one co-moving neighbor
by our selection. We provide the TGAS source id, which may be used to easily
retrieve cross matches of \gaia\ with other surveys
using the \gaia\ data archive (\todo{cite}).
For each star, we also include the positional measurements from \tgas,
\gaia\ $G$-band and \tmass\ $J$, $H$-band magnitudes as well as
\rave\ radial velocities.
The co-moving relationship between the stars is described in the pair table.
We also list the angular and physical separation of pairs, and the likelihood ratio,
$\ln \mathcal{L}_1 /\mathcal{L}_2>6$ (see \eqname~\ref{eq:hyp1} and \ref{eq:hyp2})
computed in this work.

>>>>

To date, thousands of candidate co-moving star pairs have been identified by
searching for stars with common proper motions
(\citealt{Poveda:1994aa,Allen:2000aa,Chaname:2004aa,
Lepine:2007aa,Shaya:2011aa,Alonso-Floriano:2015aa}).
Here, we use the recent first data release of \gaia\ which includes precise distances,
enabling us to ask whether two stars share the same \emph{physical (3D) velocity} rather than
just the projections in the proper motion space.

@@

\begin{figure*}[htbp]
  \begin{center}
    \includegraphics[width=\textwidth]{glon_d_pie.pdf}
  \end{center}
  \caption{%
    Panoramic view of co-moving pairs of stars around the Sun. This is a cylindrical
    projection of onto the Galactic plane with the Sun at the origin.
    Pairs in connected components of sizes less than 5 are connected by gray lines.
    Pair in connected components of size $\geq 5$ are plotted with a unique random color,
    and their nodes (stars) are highlighted with small black circles.
    We also show the positions of known Milky Way star clusters
    from \citet{Kharchenko:2016aa} as light blue circles of $10$~pc radius,
    and stars in OB associations from \citet{de-Zeeuw:1999aa} as
    blue crosses.
    Some of the larger connected components are clearly associated with known
    clusters, but we also discover quite a few new co-moving groups.
    \label{fig:glon_d_pairlines}}
\end{figure*}

@@

In this section, we describe our catalog of candidate co-moving pairs of stars.
For 13,058 pairs (10,606 unique stars) found in this work.
The catalog is composed of three tables of stars, pairs, and groups.
We summarize the content of each table in Table~\ref{tab:table_meta}, and
the relationships between the tables in Figure~\ref{fig:schema}.
The star table contains all 10,606 stars that has at least one co-moving neighbor
by our selection. We provide the TGAS source id, which may be used to easily
retrieve cross matches of \gaia\ with other surveys
using the \gaia\ data archive.
For each star, we also include the positional measurements from \tgas,
\gaia\ $G$-band and \tmass\ $J$, $H$-band magnitudes as well as
\rave\ radial velocities.
The co-moving relationship between the stars is described in the pair table.
We also list the angular and physical separation of pairs, and the likelihood ratio,
$\ln \mathcal{L}_1 /\mathcal{L}_2>6$ (see \eqname~\ref{eq:hyp1} and \ref{eq:hyp2})
computed in this work.
